HyperLogLog: Exponentially Bad in Adversarial Settings

### 2022-02-05 docs/HLL_exp_bad/main.tex
align c title
adding a cdot

With $2^{t-1}m \ln m$ honest insertions, it is also highly likely that the small range correction (Hit Counting algorithm) will not be used, and the target HLL's cardinality estimate will be computed using the raw estimate.
%\[
%E = \alpha_mm^2\cdot(\sum_{j=1}^m2^{-M[j]})^{-1}.
%\]

@@

\begin{table*}[htp]
\caption{Attacks on empty sketches for a classic HLL implementation, averaged over 50 iterations.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} |}
	\hline
	\textbf{Scenario} &  \multicolumn{2}{c|}{S1} & S2 & S4  \\ \hline
	\textbf{Original Card. Est.} & 0 & 0 &  0  & 0   \\ \hline
	\textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & 1 &  1 \\ \hline
	\textbf{\# Items added} & 4,132 & 523,791  & 4,106 & 4,106 \\ \hline
	\textbf{Final Card. Est.} & 1 & 177 & 1  & 1 \\ \hline
	\textbf{\# Resets} & 4,718 & 6,973 & - & - \\ \hline
\end{tabular}
\end{center}
\label{table:tab1}
\end{table*}%

@@

\begin{table*}[tb!]
\caption{Comparison of attack results in the S1 adversarial scenario, in the setting of~\cite{hllvuln}.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} |}
    \hline
    \textbf{Attack} & \multicolumn{2}{c|}{Ours} & ~\cite{hllvuln} \\ \hline
      \textbf{Original Card. Est.} & 0 & 0 & 0  \\ \hline
       \textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & - \\ \hline
     \textbf{\# Items added} & 977 & 125,091 & 74,390 \\ \hline
    \textbf{Final Card. Est.} & 1 & 177 &  15,780 \\ \hline
    \textbf{\# Resets} & 1,148 & 1,655 & 3 \\ \hline

>>>>

With $2^{t-1}\cdot m \ln m$ honest insertions, it is also highly likely that the small range correction (Hit Counting algorithm) will not be used, and the target HLL's cardinality estimate will be computed using the raw estimate.
%\[
%E = \alpha_mm^2\cdot(\sum_{j=1}^m2^{-M[j]})^{-1}.
%\]

@@

\begin{table*}[htp]
\caption{Attacks on empty sketches for a classic HLL implementation, averaged over 50 iterations.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} |}
	\hline
	\textbf{Scenario} &  \multicolumn{2}{c|}{S1} & \multicolumn{1}{c|}{S2} & \multicolumn{1}{c|}{S4}  \\ \hline
	\textbf{Original Card. Est.} & 0 & 0 &  0  & 0   \\ \hline
	\textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & 1 &  1 \\ \hline
	\textbf{\# Items added} & 4,132 & 523,791  & 4,106 & 4,106 \\ \hline
	\textbf{Final Card. Est.} & 1 & 177 & 1  & 1 \\ \hline
	\textbf{\# Resets} & 4,718 & 6,973 & - & - \\ \hline
\end{tabular}
\end{center}
\label{table:tab1}
\end{table*}%

@@

\begin{table*}[tb!]
\caption{Comparison of attack results in the S1 adversarial scenario, in the setting of~\cite{hllvuln}.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} |}
    \hline
    \textbf{Attack} & \multicolumn{2}{c|}{Ours} &\multicolumn{1}{c|}{~\cite{hllvuln}} \\ \hline
      \textbf{Original Card. Est.} & 0 & 0 & 0  \\ \hline
       \textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & - \\ \hline
     \textbf{\# Items added} & 977 & 125,091 & 74,390 \\ \hline
    \textbf{Final Card. Est.} & 1 & 177 &  15,780 \\ \hline
    \textbf{\# Resets} & 1,148 & 1,655 & 3 \\ \hline
